\begin{thebibliography}{}
%1
\bibitem{Mazzitelli} \textsc{Mazzitelli, Javier}.\textit{Efectos de la cromodin\'amica cu\'antica en la f\'isica
del bos\'on de Higgs.}
\textup{Tesisi doctoral, Universidad de Buenos Aires. P\'ags. 11$-$15, 2016}

%2
\bibitem{particulasgriphys} \textsc{David Griffiths}.\textit{INTRODUCTION TO ELEMENTARY PARTICLES.}
\textup{Reed College. P\'ags. 189$-$296}

%3
\bibitem{ivan} \textsc{Ivan Romo}. \textit{Estudio de la estructura de la secci\'on eficaz diferencial el\'astica $\bar{p}p-p$ a partir de un modelo quark-diquark y con una parametrizaci\'on general.}
\textup{Tesis pregrado, Universidad de Nari\~no, Colombia}, p\'ags. 3$-$10, 2015.

%4
\bibitem{carlosavila} \textsc{Carlos Avila Bernal (2013).} \textit{Colisiones el\'asticas y secci\'on eficaz total hadr\'on-hadr\'on a altas energ\'ias}.
\textup{Revista de la academia colombiana de Ciencias Exactas, F\'isicas y Naturales. Diciembre 2014. }\href{https://www.raccefyn.co/index.php/raccefyn/article/viewFile/151/62}{\texttt{Rev. Acad. Colomb. }}

%5
 \bibitem{grichine} \textsc{V.M. Grichine.}
 \textit{Nucleon elastic scattering in quark-diquark representation with
springy Pomeron}. \textup{Lebedev Physical Institute, Moscow, Russia, 2014}.\\
 \href{https://arxiv.org/abs/1404.5768v1}{arXiv:1404.5768}
 
%6 
 \bibitem{modeloqQ} \textsc{V.M. Grichine, N.I. Starkov y N.P. Zotov.}
 \textit{Quark-diquark model for $p(\bar{p})-p$ elastic scattering at high
energies}. \textup{Eur. phys. J. C73 (2013)2320}.\\
 \href{http://lanl.arxiv.org/abs/1212.2111v2}{\texttt{arXiv:1212.2111}}

%%7
\bibitem{alice} \textsc{ALICE Colaboration (2008)}.\textit{The ALICE Experiment at the CERN Large Hadron Collider.}
\textup{Institute of phisys Publishing and SISSA.}

%8
\bibitem{atlas} \textsc{ATLAS Colaboration (2008)}.\textit{The ATLAS Experiment at the CERN Large Hadron Collider.}
\textup{Institute of phisys Publishing and SISSA.}
%9
\bibitem{cms} \textsc{CMS Colaboration (2008)}.\textit{The CMS Experiment at the CERN Large Hadron Collider.}
\textup{Institute of phisys Publishing and SISSA.}

%10
\bibitem{lhcb} \textsc{LHC\textup{b} Colaboration (2008)}.\textit{The LHC\textup{b} Experiment at the CERN Large Hadron Collider.}
\textup{Institute of phisys Publishing and SISSA.}
%11
\bibitem{topicslch} \textsc{topics LHC}. \href{http://home.web.cern.ch/ ,28-07-2017}{\texttt{home.web.cern}}
%12
\bibitem{links}
 \href{http://totem.web.cern.ch/Totem}{\texttt{http://totem.web.cern.ch/Totem}} 


%13
\bibitem{links1}
 \href{http://www.ge.infn.it/totem/index.html}{\texttt{http://www.ge.infn.it/totem/index.html}} 
 %%toca por aqui
  
 
 %14
\bibitem{tesiscern2013} \textsc{Maria Kuhn.} \textit{Emittance Preservation at the
LHC.}
\textup{University of Hamburg
March 2013.}\href{http://inspirehep.net/record/1296496/files/CERN-THESIS-2013-031.pdf}{\texttt{CERN-TESIS-2013}}
%15
\bibitem{tesiscern2010} \textsc{Dominik Mierzejewski.} \textit{Roman Pot Detector Modelling and Proton
Reconstruction in the TOTEM Experiment at the LHC.}
\textup{Tesis CERN, 2010.}\href{https://cds.cern.ch/record/1319606/files/CERN-THESIS-2010-177.pdf}{\texttt{CERN-TESIS-2010}}
 
 %16
  \bibitem{plasmagluon}Stanislaw Mrowczynski. Quark-Gluon Plasma. Poland and Institute of Physics, Pedagogical University.
 \href{https://arxiv.org/pdf/nucl-th/9905005.pdf}{\texttt{arXiv:nucl-th/9905005}}
 %17
  \bibitem{beautq}Rhorry Gauld, Ulrich Haisch. Beauty-quark and charm-quark pair production asymmetries at LHCb, Pedagogical University.
 \href{https://journals.aps.org/prd/pdf/10.1103/PhysRevD.92.034007}{\texttt{PhysRevD.92.034007}}
 %18
  \bibitem{moedal}THE MoEDAL COLLABORATION.
 \href{https://arxiv.org/abs/1604.06645}{\texttt{arXiv:1604.06645}}
 
 %19
 
\bibitem{atlas}Delivered Luminosity versus time for 2011-2017 (p-p data only) Luminosity ATLAS Public Results 
 \href{https://twiki.cern.ch/twiki/bin/view/AtlasPublic/WebHome}{\texttt{https://twiki.cern.ch}} 
 %20
 \bibitem{cms}Public CMS Luminosity Information  
 \href{https://twiki.cern.ch/twiki/bin/view/CMSPublic/LumiPublicResults}{\texttt{https://twiki.cern.ch}}
 
 
 %21
 \bibitem{links3}
 \href{https://www.lch-closer.es}{\texttt{https://www.lch-closer.es}}
 %22
\bibitem{luisdelapeya} \textsc{Luis de la Pe\~na.} \textit{Introducci\'on a la mec\'anica cu\'antica}.
\textup{Tercera edici\'on, Fondo de la cultura econ\'omica, M\'exico, DF, 2006, p\'ags. 723$-$749.}




\bibitem{griphys} \textsc{David J. Griffiths.} \textit{Introduction to Quantum Mechanics.}.
\textup{Second published, Pearson Prentice Hall, United States of America, 2005, p\'ags. 394$-$405.}

\bibitem{varone} \textsc{Vincenzo Barone \textup{y} Enrico Predazzi.} \textit{High-Energy Particle Diffraction}.
\textup{First published, Springer, Germany, 2002, p\'ags. 35$-$52, 83$-$104.}

\bibitem{donachie} \textsc{S. Donnachie, G. Dosch, P. Landshoff y O. Nachtmann.} \textit{Pomeron Physics and QCD}.
\textup{First published, Cambridge, New York, 2002, p\'ags. 1$-$6, 47$-$60.}

\bibitem{ferrer} \textsc{Antonio Ferrer Soria y Eduardo Ros Mart\'inez.} \textit{Fisica de part\'iculas y astropart\'iculas}.
\textup{Segunda edici\'on, Universidad de Valencia, 2005, p\'ags. 369$-$371}

\bibitem{constanteacoplo} \textsc{The CMS Collaboration.}
 \textit{Measurement of the inclusive 3-jet production differential
cross section in proton-proton collisions at 7 TeV and
determination of the strong coupling constant in the  TeV
range}.
\href{https://arxiv.org/abs/1412.1633}{\texttt{arXiv:1412.1633}}

\bibitem{harveybyron} \textsc{Harvey Byron Meyer}
 \textit{Glueball Regge trajectories}. \textup{Lincoln College, Oxford, 2005}. \href{https://arxiv.org/abs/hep-lat/0508002v1}{\texttt{	arXiv:hep-lat/0508002}}
 


 


 \bibitem{martinov} \textsc{E. Martynov.}
 \textit{Proton (antiproton) elastic scattering at energies from FNAL to LHC
in the tripole pomeron-odderon model}. \textup{Bogolyubov Institute for Theoretical Physics, 03680 Kiev, Ukraine, 2013.} \href{https://arxiv.org/abs/1305.3093v1}{\texttt{arXiv:1305.3093}}


 \bibitem{manualroot} \textsc{User's Guide.}
 \textit{ROOT User's Guide: 6 Release Cycle}.\\
 \href{https://root.cern.ch/guides/users-guide}{\texttt{https://root.cern.ch/guides/users-guide}}
 
  \bibitem{seccioneficaztotal} \textsc{PDG part\'icle data group.}
 \textit{Data files and plots of cross-sections and related quantities
in the 2014 Review of Particle Physics}. \textup{Hadron(photon)-hadron(photon) collisions.} \href{http://pdg.lbl.gov/2014/hadronic-xsections/}{\texttt{http://pdg.lbl.gov/2014/hadronic-xsections/}}


 \bibitem{amaldi}\textsc{U. AMALDI.}
 \textit{Impact parameter interpretation of proton-proton scattering from a critical review of all ISR data.} \textup{CERN, Geneva, Switzerland.}
 \href{http://hermes.ihep.su:8001/pool/mass/jou/np_166_301.pdf}{\texttt{http://hermes.ihep.su:8001}}
 

 \bibitem{schlein}\textsc{UA8 Collaboration.}
 \textit{A Study of Inclusive Double$-$Pomeron$-$Exchange in $p(\bar{p})\rightarrow pX\bar{p}$ at root s = 630 GeV.}
 \textup{Centre d'Etudes Nucleaires-Saclay, 91191 Gif-sur-Yvette, France.}
 \href{https://arxiv.org/abs/hep-ex/0205037v3}{\texttt{arXiv:hep-ex/0205037}} 
 
  \bibitem{metricavariable}\textsc{WILLIAM C. DAVIDON.}
 \textit{VARIABLE METRIC METHOD FOR MINIMIZATION.}
 \textup{Vol. 1, No. 1, pp. 1-17, February 1991.}
 \href{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.693.272&rep=rep1&type=pdf}{\texttt{SIAM J. OPTIMIZATION Vol. 1}} 
 
 
   \bibitem{minuit}\textsc{Fred JAMES
and
Matthias WINKLER
CERN, Geneva.}
 \textit{MINUIT User's Guide.}
 \textup{June 16, 2004.}
 \href{http://inspirehep.net/record/1258345/files/mnusersguide.pdf}{\texttt{MINUIT-User's-Guide}}
 
 \bibitem{guialab} \textsc{Yithsbey Giraldo, Fredy Santacruz.}\textit{Guia de Laboratorio de F\'isica 1.}
\textup{Universidad de Nari\~no. P\'ags. 3$-$10. ISBN:978-958-8609-44-7}
 
 
\end{thebibliography}